%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Sebastian} % Your first name
\familyname{Castillo} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Crr79A 53A-32 ap401}{Medellin, Colombia}
\mobile{(+57) 300 603 59 94}
\email{sebastian@nullindustries.co}
\homepage{http://github.com/scastillo}{github/scastillo} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{additional information}

\quote{"You will be free hackers, you will be free" - R. Stallman}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\section{}
\cventry{Zerply}{http://zerp.ly/castillobuiles}{}{}{}{}
\cventry{LinkedIn}{http://co.linkedin.com/pub/sebastian-castillo/1a/5a1/862}{}{}{}{}
\cventry{Twitter}{http://twitter.com/castillobuiles}{}{}{}{}
\cventry{HN}{http://news.ycombinator.com/user?id=scastillo}{}{}{}{}
\cventry{Github}{http://github.com/scastillo}{}{}{}{}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2004--2008}{Computer Sc.}{Universidad EAFIT}{Medellin}{}{Logic and computation group member, Software engineering monitor, High availability architecture designer}  % Arguments not required can be left empty

\subsection{Research}
\cventry{2007}{Hardware Model Driven Development MDA}{Universidad de antioquia}{}{Automatic code generation UML2.0 => SystemC}{}

\section{Other studies}
\cventry{2008}{}{CMMI v1.2}{Official SEI course}{}{}{}
\cventry{2005}{}{Mobile applications development with J2ME}{Universidad EAFIT}{}{}{}
\cventry{2007}{}{Cisco Certified Network Associate CCNA}{Universidad EAFIT}{}{}{}
\cventry{2006}{}{Linux server routing}{Universidad EAFIT}{}{}{}
\cventry{2002}{}{Java OOP}{Universidad Nacional}{}{}{}

\section{I have been speaker at}
\cventry{2011}{Sexy Continuous Integration}{CMMI v1.2}{Official SEI course}{}{}{}
\cventry{2011}{How to build an entrepreneurs network (CoffeeGrid)}{DELM}{Jardin Botanico}{}{}{}
\cventry{2010}{Virtual payment methods with paymentez}{GAE Summit}{Google HQ, Palo Alto}{}{}{}
\cventry{2010}{Unit testing for Google App Engine}{Paymentez Summit}{Mentez LLC}{}{}{}
\cventry{2010}{Intro to security architectures and SABSA}{Primary group}{Fluidsignal}{}{}{}
\cventry{2009}{Hands on: Man in the middle attacks with ARP poison}{Security week conferences}{CSM}{}{}{}


\section{I have teach the following courses}
\cventry{2008}{Operative systems and GNU-Linux}{Universidad EAFIT}{Catedra emrpesarial}{}{}{}
\cventry{2009}{Penetration testing and information security}{Universidad EAFIT}{Cryptography, owasp top 10, ARP poison, SSH MiM, ISO27k}{}{}{}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{2014}{Founder, lead dev}{\textsc{ContextSurgery}}{http://contextsurgery.com}{}{
Google glass for surgeons.
\begin{itemize}
\item High available architecture development and design. (salt + docker deployment, multi cloud providers)
\item Scrum-like life-cycle implementation. (trello + pivotaltracker)
\item Node (js/coffeescript) rest api + SOA architecture (python).
\item Continuous deployment config and operation (jenkins + hubot).
\item Single page app with backbone.js
\item XMPP live chat
\item WebRTC video conference rooms
\item Glass app
\end{itemize}
}

\cventry{2014}{Founder, lead dev}{\textsc{Geniusly}}{http://geniusly.com}{}{
Truck management system.
\begin{itemize}
\item High available architecture development and design. (salt deployment, multi cloud providers)
\item Scrum-like life-cycle implementation. (trello + pivotaltracker)
\item Node (js/coffeescript) rest api + SOA architecture (python).
\item Continuous deployment config and operation (jenkins + hubot).
\item Single page app with backbone.js
\end{itemize}
}

\cventry{2013}{lead dev}{\textsc{ScreenMedix}}{http://geniusly.com}{}{
Google glass repair in real time.
\begin{itemize}
\item Redis pub/sub
\item High available architecture development and design. (salt deployment, multi cloud providers)
\item Scrum-like life-cycle implementation. (trello + pivotaltracker)
\item Continuous deployment config and operation (jenkins + hubot).
\item Single page app with backbone.js
\end{itemize}
}

\cventry{2012--2013}{Founder}{\textsc{Engager}}{http://engager.io}{}{
OKCupid for developers and companies.
\begin{itemize}
\item Ruby/Rails web app
\item Single page app with backbone.js
\end{itemize}
}

\cventry{2013}{Founder, cto}{\textsc{Nuage}}{}{}{
Platform as a service PaaS for django web apps.
\begin{itemize}
\item Django web api
\item High available architecture development and design. (Puppet deployment, multi cloud providers)
\item Scrum-like life-cycle implementation. (trello + pivotaltracker)
\item Continuous deployment config and operation (jenkins + hubot).
\item Single page app with backbone.js
\item Lunix containers
\end{itemize}
}

\cventry{2012}{Lead developer}{\textsc{Tourvox}}{}{}{
Mobile marketplace for tourists and tour guides.
\begin{itemize}
\item High available architecture development and design.
\item Scrum-like life-cycle implementation.
\item Django-nonrel + Mongo + GEO rest api development
\item Wikipedia scrapping background task
\item Continuous deployment config and operation
\end{itemize}
}

\cventry{2010--2012}{Lead developer}{\textsc{Mentez LLC}}{}{}{
\begin{itemize}
\item High available architecture development and design (1200 hits/sec, 2M users)
\item Scrum-like life-cycle implementation \& scrum master.
\item Continuous deployment config and operation
\end{itemize}
}

\cventry{2006--2011}{Projects engineer}{\textsc{Fluidsignal Group}}{}{}{
\begin{itemize}
\item Sofware developer
\item Penetration tester
\item ISO27000 and CMMI consultor
\item Research and development leader
\item Best practices consultant (itil, iso2700, iso9000, cmmi)
\item Security code reviewer
\item Social Engineering
\end{itemize}
}


\subsection{Vocational}

\cventry{2010--Present}{Founder, Director}{\textsc{CoffeeGrid}}{Medellin}{}{
http://coffeegrid.org\newline{}
CoffeeGrid is the Alcoholics Anonymous of entrepreneurship in Medellin.\newline{}
A space, a community, a monthly commited bunch of entrepreneurs, developers, caffein adicts, citizens looking for what to do the last wednesday of each month.\newline{}
CoffeeGrid inspire and digg entrepreneurship in local spaces, putting all together in an organic, independent and opinionated way that only we can do.\newline{}
You can find here a co-founder, an idea, an ispiration, a free coffee, a beer or a soul mate.
\newline{}\newline{}
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item More than 16 events in 3 years
\item More than 30 special guests sharing with the local community
\item Near 8 projects growing from CoffeeGRid Feedback
\item Pioneering community have inspired the fertil ecosystem we have today
\end{itemize}
}
\cventry{2007}{Deabian project developer}{}{}{}{SIPCrack}

%------------------------------------------------

\cventry{2012}{Startup Weekend Organizer}{Medellin}{}{}{First BIG Startup Weekend in town, with more than 120 assitants and international mentors}

\cventry{2012}{Dev Med}{Founder}{Medellin}{}{Local developers meetup\newline{}
http://devmed.herokuapp.com/
}

\cventry{2012}{Startup Weekend Organizer}{Medellin}{}{}{First BIG Startup Weekend in town, with more than 120 assitants and international mentors}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2013}{Startup Weekend Medellin 1st place (Elegidos: A mobile app to call a designed driver "uber for drunk guys"}
\cvitem{2011}{Startup Weekend Bogota 1st place (BeBtr: Virtual bets mobile app)}



\section{Press}

\cvitem{2009}{El Colombiano}{How to protect yourself against Bluethoot hackers (bluejackong)}{}{}{}{}{}

\cvitem{2009}{Teleantioquia News}{Introduction to smart devices}{}{}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Intermediate}{\textsc{iOS}, \textsc{Android}, \LaTeX}
\cvitem{Advanced}{Python, node.js, backbone.js, Linux, High available architectures, and go linkedin to see more}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Spanish}{Mothertongue}{}
\cvitemwithcomment{English}{Advanced}{Conversationally fluent}
\cvitemwithcomment{Dutch, French}{Really basic}{I can go and buy milk but i'd love learning more}



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}